Brief notes on erosion

### 2017-03-22 docs/Notes.tex
NM
Removed all instances of the parameter beta. Instead I am using the function cdfscale to scale the curvature-driven flow how I like. For 2D Stokes flow, cdfscale should be -1/Log(L).
writing notes on scaling the smoothing term

\subsubsection{Different scaling of the stress}
Some numerical tests reveal that the stress scales like $\tau \sim 1/(L \log L)$, instead of the naive $1/L$. This might because we are in a 2D bounded domain (Stokes paradox type stuff). So we need to modify the curvature driven flow to have the same scaling. To this end, modify Eq.~(\ref{Vn1}) to read
\begin{equation}
V_n = \atau + \eps f(L) \left(\kappa - \frac{2 \pi}{L} \right)
\end{equation}
where for 2D Stokes flow, we will have $f(L) = -1/\log L$. Carrying through this change, Eq.~(\ref{Vn2}) becomes
\begin{equation}
V_n = \atau + \eps L^{-1} f(L) \left(\pd{\theta}{\alpha} - 2 \pi \right)
\end{equation}
and Eq.~(\ref{thetaEvolve}) becomes
\begin{equation}
\pd{\theta}{t} = \eps L^{-2} f(L) \ppd{\theta}{\alpha} + L^{-1} \left( \pd{\atau}{\alpha} + \pd{\theta}{\alpha} V_s \right)
\end{equation}
Then to evolve $\theta$ spectrally, we use
\begin{equation}
\td{\thh_k}{t} + 4 \pi^2 k^2 \eps L^{-2} f(L)  \thh_k = \hat{N}_k
\end{equation}

>>>>

\subsection{Different scaling of the stress}
Some numerical tests reveal that the stress scales like $\tau \sim 1/(L \log L)$, instead of the naive $1/L$. This might because we are in a 2D bounded domain (Stokes paradox type stuff). So we need to modify the curvature driven flow to have the same scaling. To this end, modify Eq.~(\ref{Vn1}) to read
\begin{equation}
V_n = \atau + \eps f(L) \left(\kappa - \frac{2 \pi}{L} \right)
\end{equation}
where for 2D Stokes flow, we will have $f(L) = -1/\log L$. Carrying through this change, Eq.~(\ref{Vn2}) becomes
\begin{equation}
V_n = \atau + \eps L^{-1} f(L) \left(\pd{\theta}{\alpha} - 2 \pi \right)
\end{equation}
and Eq.~(\ref{thetaEvolve}) becomes
\begin{equation}
\pd{\theta}{t} = \eps L^{-2} f(L) \ppd{\theta}{\alpha} + L^{-1} \left( \pd{\atau}{\alpha} + \pd{\theta}{\alpha} V_s \right)
\end{equation}
Then to evolve $\theta$ spectrally, we use
\begin{equation}
\td{\thh_k}{t} + 4 \pi^2 k^2 \eps L^{-2} f(L)  \thh_k = \hat{N}_k
\end{equation}
where the nonlinear terms are grouped together as
\begin{equation}
N = L^{-1} \left( \pd{\atau}{\alpha} + \pd{\theta}{\alpha} V_s \right)
\end{equation}
We evolve with the integrating-factor method. When recast in terms of Gaussian filters, this gives
\begin{equation}
\label{intfact}
\thh^{(n+1)} = \GG(\theta^{(n)}, \sigma_1) 
+ \frac{\Dt}{2} \left( 3 \GG(N^{(n)}, \sigma_1) - \GG(N^{(n-1)}), \sigma_2 \right)
\end{equation}
where
\begin{align}
& \sigma_1 = 2 \pi \sqrt{\eps \Dt} \sqrt{g(L^{n}) + g(L^{n+1}) } 	\\
& \sigma_2 = 2 \pi \sqrt{\eps \Dt} \sqrt{g(L^{n-1}) + 2 g(L^{n}) + g(L^{n+1}) }
\end{align}
where $g(L) = L^{-2} f(L)$.
%This will also modify the scaling law for area vs time!!!

\vsp{2}
{\bf  Alternative}: Perhaps I just want to calculate the mean of the shear stress directly and use it to scale the curvature driven flow. This idea gives
\begin{equation}
V_n = \atau + \eps \mean{\atau} \left(\kappa - \frac{2 \pi}{L} \right)
\end{equation}
which gives
\begin{equation}
V_n = \atau + \eps L^{-1} \mean{\atau} \left(\pd{\theta}{\alpha} - 2 \pi \right)
\end{equation}
Then we get
\begin{equation}
\pd{\theta}{t} = \eps L^{-2} \mean{\atau} \ppd{\theta}{\alpha} + L^{-1} \left( \pd{\atau}{\alpha} + \pd{\theta}{\alpha} V_s \right)
\end{equation}
Then to evolve $\theta$ spectrally, we use
\begin{equation}
\td{\thh_k}{t} + 4 \pi^2 k^2 \eps L^{-2} \mean{\atau}  \thh_k = \hat{N}_k
\end{equation}
Then the Gaussian filter stuff becomes
\begin{equation}
\label{intfact}
\thh^{(n+1)} = \GG(\theta^{(n)}, \sigma_1) 
+ \frac{\Dt}{2} \left( 3 \GG(N^{(n)}, \sigma_1) - \GG(N^{(n-1)}), \sigma_2 \right)
\end{equation}
where
\begin{align}
& \sigma_1 = 2 \pi \sqrt{\eps \Dt} \sqrt{g^{n} + g^{n+1} } 	\\
& \sigma_2 = 2 \pi \sqrt{\eps \Dt} \sqrt{g^{n-1} + 2 g^{n} + g^{n+1} }
\end{align}
where $g(t)= L^{-2} \mean{\atau}$ and $g^{(n)} = g(t^{(n)})$.
BUT the problem with this is that I do not yet know $\mean{\atau}$ at time-step $n+1$, so I would have to change my time-stepping strategy which is a significant change to the code structure. Thus, I prefer the first method of using $L \log L$.
